Age-related changes in plant growth and traits

### 2015-08-17 Growth_figs.rmd
Embed derived quntities into remake workflow
Closes #18

Squashed commit of the following:

commit f868cdc0b9638356f9e65a5188b2aa58865e840f
Author: Daniel Falster <daniel.falster@mq.edu.au>
Date:   Mon Aug 17 16:01:37 2015 +1000

    averages by species and patch age

commit 1030d59fd886f0f680620b0dd2761db14eb506eb
Author: Daniel Falster <daniel.falster@mq.edu.au>
Date:   Mon Aug 17 13:51:01 2015 +1000

    Remove as.factor

commit 6b94e4820873bd85e838013782e451e9c3d021c3
Author: Daniel Falster <daniel.falster@mq.edu.au>
Date:   Mon Aug 17 13:50:46 2015 +1000

    Remove some outdated stuff

c

plot(WD_mean~leaf_area_growth,SummaryInd,log="y",pch=16,col=col.age[as.factor(age)])
mod <- lm(log(leaf_area_growth)~age*WD_mean,SummaryInd)
summary(mod)
```

>>>>

plot(wood_density~leaf_area_growth,SummaryInd,log="y",pch=16,col=col.age[as.factor(age)])
mod <- lm(log(leaf_area_growth)~age*wood_density,SummaryInd)
summary(mod)
```
